Detection of Oscillations in Aldebaran with Ground-Based Observations

### 2017-09-29 paper/aldebaran.tex
tidy introduction
added an abstract

\begin{abstract}
Stuff.
\end{abstract}

@@

In order to verify the results of the novel analysis presented above, we sought to obtain an independent detection of the oscillations of Aldebaran and compare the frequencies determined with the two methods. 
Aldebaran was therefore observed with \ktwo \citep{howell14}, a two-wheeled revival of the \kepler Mission \citep{2010sci...327..977b}, under Guest Observer Program 130471 in Campaign~13, from 2017-03-08 to 2017-05-27.

>>>>

\begin{abstract}
The nearby red giant Aldebaran is suspected to host a gas giant planetary companion from decades of ground-based spectroscopic measurements of its Doppler shift. Using Gaussian Process based Continuous Auto-Regressive Moving Average (CARMA) models, we confirm this suspected planet and show that this historic data also contains evidence of acoustic oscillations in the star itself, and verify this result with further dedicated ground-based spectroscopy and space-based photometry with the \kepler Space Telescope. From the frequency of these oscillations we determine the mass of Aldebaran to be $1.16 \pm 0.07$~\msun, and note that this implies its planet will have been subject to insolation comparable to the Earth for some of the star's main sequence lifetime. Our approach to sparse, irregularly sampled time series astronomical data has the potential to unlock similar measurements for hundreds of stars in archival data, and permits more flexible observing schedules in future. 
\end{abstract}

@@

In order to verify the results of the novel analysis presented above, we sought to obtain an independent detection of the oscillations of Aldebaran and compare the frequencies determined with the two methods. 
Aldebaran was therefore observed with \ktwo \citep{howell14}, a two-wheeled revival of the \kepler Mission \citep{2010sci...327..977b}, under Guest Observer Program 130471 in Campaign~13, from 2017-03-08 to 2017-05-27. Aldebaran and similar K giants are known to be photometrically variable from Hipparcos photometry \citep{bedding2000}, and we sought to obtain higher-precision, continuous light curves to compare to our CARMA results.
